An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$

### 2019-12-31 paper.tex
Correct the statement of length of MAM channel and endpoint

With proper tuning factor, we can derive payoff function which is similar to Figure \ref{fig:payoff_pic}. The red dot in this figure indicates the data quality that data provider would most likely provide, since the data provider can achieve maximum payoff at that point. Namely, the red dot is the Nash Equilibrium of this game theory model. Both scales of x-axis and y-axis have been normalized. X-axis is normalized into a range between 0 to 100 which can reflect customer satisfaction of data buyers, y-axis is normalized into a range between -1 and 1.

@@

\subsubsection{Channel / Endpoint Creation}
The length of a channel or endpoint is $2^{height}$ where \textit{height} is the height of Merkle Hash Tree in Merkle signature scheme (MSS). A channel with height $n$ can create $2^n$ endpoints, and an endpoint with height $m$ can attach $2^m$ messages, therefore the capacity of a channel is $2^{nm}$ messages in total. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data. The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}. The time duration for each \textit{height} is the average time of running 100 rounds.

>>>>

The red dot in Figure \ref{fig:payoff_pic} indicates the data quality that data provider would sustain, since the data provider can achieve maximum payoff at that point. Namely, the red dot is the Nash Equilibrium of this game theory model.

@@

\subsubsection{Channel / Endpoint Creation}
The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in Merkle signature scheme (MSS) ,and the substracted $1$ is for announcing the ID of next channel or endpoint. A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data. The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}. The time duration for each \textit{height} is the average time of running 100 rounds.
